### 2015-01-07 paper/paper.tex
autocommit 01/07 15:57

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_20_mst_walltime.png}
		\label{fig:tsp_20_mst}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_roundtrip_walltime.png}
		\label{fig:tsp_13_round}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_blind_walltime.png}
		\label{fig:tsp_13_blind}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの実行速度の比較}
\end{figure}%

@@

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_20_mst_expd.png}
		\label{fig:tsp_20_mst_expd}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_roundtrip_expd.png}
		\label{fig:tsp_13_round_expd}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{speedup/tsp_13_blind_expd.png}
		\label{fig:tsp_13_blind_expd}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの探索ノード数の比較}
\end{figure}%-

>>>>

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{ruby.png}
		\label{fig:tsp_20_mst}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{ruby.png}
		\label{fig:tsp_13_round}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{ruby.png}
		\label{fig:tsp_13_blind}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの実行速度の比較}
\end{figure}%

@@

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{ruby.png}
		\label{fig:tsp_20_mst_expd}
		\caption{TSP with minimum spanning tree (20 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{ruby.png}
		\label{fig:tsp_13_round_expd}
		\caption{TSP with Round-trip distance (13 cities)}
	\end{subfigure}

	\begin{subfigure}{0.6\columnwidth}
		\includegraphics[width=\columnwidth,draft]{ruby.png}
		\label{fig:tsp_13_blind_expd}
		\caption{TSP with blind (13 cities)}
	\end{subfigure}
	\label{fig:comparison}
	\caption{HDA*とPBNFの探索ノード数の比較}
\end{figure}%-
